The ChEMBL database as Linked Open Data

### 2013-03-06 article.tex
Removed the last 'indeed'
Listed the references at the first occurance of the resource too.

To integrate ChEMBL-RDF with RDF versions of other scientific datasets, we link out to various resources.
These links are shown in Figure~\ref{2}. Triples for compounds link out to ChemSpider 
using the complementary index and OpenMolecules RDF using InChI values. Protein links are given to Bio2RDF~\cite{Belleau2008}
using the UniProt identifier~\cite{TheUniProtConsortium2010}. Literature references are directed to CrossRef and Bio2RDF 
using the DOIs and PubMed identifiers, respectively.

@@

Much could be argued about the choice of ontologies, and the lack of an
ontology in places where we decided to use custom classes and predicates. Indeed, the
choices have only partly been decided using ontological arguments. Most of the choices are based
on pragmatic approaches to enable solutions to the range of use cases we describe here. It should be noted,
however, that the ChEMBL database captures a wide variety of experimental studies
and that semantics are not fully specified in the primary source from which the ChEMBL data was
extracted. As it is not possible to infer the original intentions in these cases, 
it is our opinion that it is better to leave some semantics undefined. During the 
development of the applications some incorrect assumptions have been discovered and
fixed, but in the main we have tried to avoid making assumptions if they are not generally known to be valid. 
Therefore, the goal of this work is the conversion of the ChEMBL data into
RDF, and not an ontological modeling of the domain.

>>>>

To integrate ChEMBL-RDF with RDF versions of other scientific datasets, we link out to various resources.
These links are shown in Figure~\ref{2}. Triples for compounds link out to ChemSpider 
using the complementary index and OpenMolecules RDF using InChI values~\cite{Pence2010,Bradley2009,Willighagen2011}.
Protein links are given to Bio2RDF~\cite{Belleau2008}
using the UniProt identifier~\cite{TheUniProtConsortium2010}. Literature references are directed to CrossRef and Bio2RDF 
using the DOIs and PubMed identifiers, respectively~\cite{Bilder2011}.

@@

Much could be argued about the choice of ontologies, and the lack of an
ontology in places where we decided to use custom classes and predicates. These
choices have only partly been decided using ontological arguments. Most of the choices are based
on pragmatic approaches to enable solutions to the range of use cases we describe here. It should be noted,
however, that the ChEMBL database captures a wide variety of experimental studies
and that semantics are not fully specified in the primary source from which the ChEMBL data was
extracted. As it is not possible to infer the original intentions in these cases, 
it is our opinion that it is better to leave some semantics undefined. During the 
development of the applications some incorrect assumptions have been discovered and
fixed, but in the main we have tried to avoid making assumptions if they are not generally known to be valid. 
Therefore, the goal of this work is the conversion of the ChEMBL data into
RDF, and not an ontological modeling of the domain.
